
```{r}
library(tidyverse)
library(here)
```

# Simulation specs

This is a simulation to compare the scaled vs unscaled embeddings. The simulation shares all the same parameters except for the values of the embeddings. The parameters are as following: 

```
BATCH_INFO = {
    "jitter_n": 1, 
    "total_batch_n": 1, 
    "jitter_mode": "sampling"
}

GRID_INFO = {
    "grid_mu_start": -4, "grid_mu_end": 4, "grid_mu_step": 5, 
    "grid_sigma_start": 0.001, "grid_sigma_end": 1.8, "grid_sigma_step": 5, 
    "grid_y_start": -4, "grid_y_end": 4, "grid_y_step": 5, 
    "grid_epsilon_start": 0.00000000001, "grid_epsilon_end": 1, "grid_epsilon_step": 5, 
    "hypothetical_obs_grid_n": 10
}


BATCH_GRID_INFO = num_stab_help.get_batch_grid(BATCH_INFO, GRID_INFO)

PRIOR_INFO = {
    "mu_prior": 1,  
    "V_prior": 1, 
    "alpha_prior": 3, 
    "beta_prior": 1, 
    "epsilon": 0.0001, "mu_epsilon":0.0001, "sd_epsilon": 0.0001, 
    "hypothetical_obs_grid_n": 5, 
    "world_EIGs": 0.00001, "max_observation": 500
}
```

And for the stimuli, the scaled stimuli are: 
```
fam: tensor([-0.2870,  0.2874,  0.3432], dtype=torch.float64) test: tensor([-0.4805, -0.9730, -0.2181], dtype=torch.float64)
```
and the unscaled are 10x of the original 
```
fam: tensor([-2.870,  2.874,  3.432], dtype=torch.float64) test: tensor([-4.805, -9.730, -2.181], dtype=torch.float64)
```

and for a milder version 4x of the orignal: 

```
fam: tensor([-1.1478,  1.1498,  1.3730], dtype=torch.float64) test: tensor([-1.9222, -3.8920, -0.8725], dtype=torch.float64)
```




Each consisted of 50 run of the same simulation, The stimuli squence are BBBBD
Below are the comparisons

```{r}
library(tidyverse)
library(here)

eig_df <- read_csv(here("scaled_vs_unscaled/eig_df.csv"))
sim_df <- read_csv(here("scaled_vs_unscaled/sim_df.csv"))
x10_eig_df <- read_csv(here("scaled_vs_unscaled/x10_eig_df.csv"))
x10_sim_df <- read_csv(here("scaled_vs_unscaled/x10_sim_df.csv"))
x4_eig_df <- read_csv(here("scaled_vs_unscaled/x4_eig_df.csv"))
x4_sim_df <- read_csv(here("scaled_vs_unscaled/x4_sim_df.csv"))

```

First let's compare the missing values of eig. From the values we can't see any clear dishabitaution in the x10 case 

```{r}
eig_df %>% 
  mutate("type" = "org") %>% 
  filter(!is.na(stimulus_id)) %>% 
  bind_rows(
    x10_eig_df %>% 
      mutate("type" = "x10") %>% 
      filter(!is.na(stimulus_id)), 
    x4_eig_df %>% 
      mutate("type" = "x4") %>% 
      filter(!is.na(stimulus_id))
  ) %>% 
  group_by(type, run_id) %>% 
  mutate(t = row_number()) %>% 
  ggplot(aes(x = stimulus_id, y = EIG)) + 
  geom_point(position = position_jitter(width=.1))+ 
  facet_wrap(~type)
  


```

we can also check on invalid values (i.e. the number of rows with EIG < 0). 



```{r}
eig_df %>% 
  filter(EIG < 0) %>% 
  count()

x4_eig_df %>% 
  filter(EIG < 0) %>% 
  group_by(stimulus_id) %>% 
  count()

x10_eig_df %>% 
  filter(EIG < 0) %>% 
  group_by(stimulus_id) %>% 
  count()
  

```


Then we can look at the trajectories. The originals doesn't look quite right, maybe due to the prior? no clear habituation but very clear dishabituation

```{r}
sim_df %>% 
  rename(stimulus_id = `...1`) %>% 
  ggplot(aes(x = stimulus_id, y = sample_n)) + 
  geom_point(alpha = .3) + 
  stat_summary(fun.data = "mean_cl_boot", color = "red") + 
  stat_summary(fun.data = "mean_cl_boot", geom = "line", color = "red") + 
  labs(title = "scaled")

x4_sim_df %>% 
  rename(stimulus_id = `...1`) %>% 
  ggplot(aes(x = stimulus_id, y = sample_n)) + 
  geom_point(alpha = .3) + 
  stat_summary(fun.data = "mean_cl_boot", color = "red") + 
  stat_summary(fun.data = "mean_cl_boot", geom = "line", color = "red") + 
  labs(title = "x4 scaled (unscaled proxy)")

x10_sim_df %>% 
  rename(stimulus_id = `...1`) %>% 
  ggplot(aes(x = stimulus_id, y = sample_n)) + 
  geom_point(alpha = .3) + 
  stat_summary(fun.data = "mean_cl_boot", color = "red") + 
  stat_summary(fun.data = "mean_cl_boot", geom = "line", color = "red") + 
  labs(title = "x10 scaled (unscaled proxy)")



```
it turns out there was no variation for the unscaled version at all. all backgrounds have 1 sample, and deviant has 2 samples. persumably due to the last trial always having negative number. 


```{r}
x10_sim_df 
```

